Predictive analytics in quality assurance for assembly processes: lessons learned from a case study at an industry 4.0 demonstration cell

### 2020-11-07 02_Paper/paper.tex
experiment text.
worked on section 3: democell

\section{The case industry 4.0 demonstration cell} % (taken from title) % 3/4 Page \OneAim doc bases
\begin{figure}
\caption{The industry simulation cell. \MW{TODO: Find image.}}
\label{fig:ind_cell}
\end{figure}

@@

\AP{
What is the demozelle and why it is relevant as study case
Description of the assemble process in the Demozelle 
Incl pictures
}
\section{Methods} %3/4 Page

>>>>

\section{The case industry 4.0 demonstration cell} % (taken from title) % 3/4 Page \OneAim doc bases

The demonstration cell is a demonstrator representing a general assembly process
and is essentially composed of assembly lines, a universal robot and a wide
range of sensor technology. The following use case is implemented:
shown is a stylized assembly process where two disks are to be stacked on top of each other.
The quality of the pseudo products is predicted on the basis of the concentricity of both
parts to be joined and the optimum operating point. The demonstration cell is configured to 
imitate certain situations that occur in real applications. For example, it is possible to 
simulate failures in the motors, problems with the conveyor belts or incorrect
positioning of an object by the robot arm, which causes anomalies in the vibration sensors,
temperature rise, fluctuations in the air pressure system and other deviations. 
Due to its manageable size and high scalability,
findings gained with the demonstration cell can be transferred to various real
assembly processes and use cases.

\begin{figure}
\caption{The industry simulation cell. \MW{TODO: Find image.}}
\label{fig:ind_cell}
\end{figure}

@@

\AP{
What is the demozelle and why it is relevant as study case
Description of the assemble process in the Demozelle 
Incl pictures
}

\section{Methods} %3/4 Page
